Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-07-25 writing/embedded_meta_learning_main.tex
Fixing bug, preprint
Starting response

@@

\begin{document}
\title{Embedded Meta-Learning: Toward more flexible deep-learning models}
\author{%
Andrew K. Lampinen\\
Department of Psychology\\
Stanford University\\
\textt{lampinen@stanford.edu}\\
\And
James L. McClelland\\
Department of Psychology\\
Stanford University\\
\textt{mcclelland@stanford.edu}\\
}
\date{}
\maketitle

@@

\[\hat{z}_{new} = F_{z_{\text{function}}}(z_{go}) \qquad \text{where } F_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]

>>>>

\PassOptionsToPackage{numbers}{natbib}

@@

\begin{document}
\title{Embedded Meta-Learning: Toward more flexible deep-learning models}
\author{%
Andrew K. Lampinen\\
Department of Psychology\\
Stanford University\\
\texttt{lampinen@stanford.edu}\\
\And
James L. McClelland\\
Department of Psychology\\
Stanford University\\
\texttt{mcclelland@stanford.edu}\\
}
\date{}
\maketitle

@@

\[\hat{z}_{new} = F_{z_{\text{meta}}}(z_{game1}) \qquad \text{where } F_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
